Many claims of group polarization are plausibly false due to inappropriate statistics

### 2022-11-20 GroupPolarizationStatmod/paper/ms.tex
ready to start on model figures for n->infty and t-test analyses

\usepackage{mathspec}
% \setallmainfonts(Digits,Latin){STIX Two Text}
% \setallmainfonts(Digits,Latin){Baskerville}
% \setallmainfonts(Digits,Latin){Plantagenet Cherokee}
\setallmainfonts(Digits,Latin){Palatino}
% \setallmainfonts(Digits,Latin){Hoefler Text}

@@

All ten studies analyzed here used an ordinal scale, but group polarization experiments seem to
lack any systematicity in experimental design beyond that. (EXAMPLES)

@@

\subsubsection{Identify null-model parameters that yield plausibly-false positives}

@@

\spacing{1.0}
\input{t-test-table.tex}
% \input{t-test-table-custom.tex}
\spacing{1.5}

>>>>

\usepackage{amsmath}
\usepackage{mathspec}
% \setallmainfonts(Digits,Latin){STIX Two Text}
% \setallmainfonts(Digits,Latin){Baskerville}
% \setallmainfonts(Digits,Latin){Plantagenet Cherokee}
\setallmainfonts(Digits,Latin){Palatino}
% \setallmainfonts(Digits,Latin){Hoefler Text}

@@

We assume that participant $i$'s internal, latent psychological opinion at 
time of reporting ($t \in \{pre, post\}$) is drawn from a normal distribution
with mean $\mu_t$ and standard deviation $\sigma_t$,
\begin{equation}
  o_{i,t} \sim \mathcal{N}(\mu_t, \sigma_t).
  \label{eq:opinionDistribution}
\end{equation}
\noindent
This is the condition-level distribution of opinions at time, $t$, chosen to
represent the common experimental design used by group polarization studies,
not because it is statistically appropriate---in fact it is not, which is what
we aim to show in this paper.

@@

We model measurement of $N \to \infty$ participant opinions,
which results in a histogram of frequency of opinions
in each bin, i.e., $o_{i,t} = b_k$. The frequency of responses in each bin is 
the integral over the continuous normal probability density function from 
one bin threshold to another. This transforms the probability density 
function from $p(o_{i,t};~\mu_t, \sigma_t)$ to the probability
of observing a reported opinion of each bin value. 
The probability of observing an opinion in bin
$b_k$ is calculated by integrating the normal probability density 
function over the range of $\theta_{k-1}$ to $\theta_{k}$. 
Formally, we write the 
probability of observing an opinion in bin $k$ at time $t$ as
\begin{equation}
\begin{aligned}
  p(o = b_k;\mu_t, \sigma_t, \theta) 
    &= \int_{\theta_{k-1}}^{\theta_k} p(o;\mu_t, \sigma_t) do \\
    &= \Phi \left( \frac{o - \mu_t}{\sigma_t} \right)\Big|_{o=\theta_{k-1}}^{\theta_k} \\
    &= \Phi \left( \frac{\theta_k - \mu_t}{\sigma_t} \right) - 
       \Phi \left( \frac{\theta_{k-1} - \mu_t}{\sigma_t} \right)
\end{aligned}
\label{eq:binFrequency}
\end{equation}
\noindent
where $\Phi(\frac{o - \mu}{\sigma})$ is the normalized 
normal cumulative distribution function over opinions $o$, shifted by an amount $\mu$ with
standard deviation $\sigma$.
\subsubsection{Identify null-model parameters that yield plausibly-false positives}

@@

\spacing{1.0}
\hspace{-1em}
\begin{center}
\input{t-test-table.tex}
\end{center}
% \input{t-test-table-custom.tex}
\spacing{1.5}
